\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-07-01 paper/subdocuments/results.Rnw
fixed issue with invisible tables (remove table env)

<<polindex20032010, results='asis'>>=
# Setup functin to produce latex tables with polarization indices and difference in ginis
polTable <- function(y, yo, ywgt=1, yowgt=1,ndig=2,title="Inequality Indices") {
stopifnot(is.numeric(y), is.numeric(yo)) # all TRUE
#y vector with new distribution
#yo vector with reference distribution
#ywgt yowgt: weights to use (optional)
#ndig: digits to display, default 2
#title: table title (optional)

# load neccessary libraries
library(reldist,quietly=TRUE,warn.conflicts=FALSE) #for Latex tables
library(Hmisc,quietly=TRUE,warn.conflicts=FALSE)

@@

latex(format(c("Median Index"=med, "Lower Index"=lower, "Upper Index"=upper, "$\\Delta$ Gini"=dgini),digits=ndig),file="",title=title)
}

polTable(bd.2010.ind,bd.2003.ind)
@

>>>>

<<poltable>>=
# Setup functin to produce latex tables with polarization indices and difference in ginis
polTable <- function(y, yo, ywgt=1, yowgt=1,ndig=2,title="Inequality Indices") {
stopifnot(is.numeric(y), is.numeric(yo)) # all TRUE
#y vector with new distribution
#yo vector with reference distribution
#ywgt yowgt: weights to use (optional)
#ndig: digits to display, default 2
#title: table title (optional)

# load neccessary libraries
library(reldist,quietly=TRUE,warn.conflicts=FALSE) #for Latex tables
library(Hmisc,quietly=TRUE,warn.conflicts=FALSE)
library(xtable,quietly=TRUE,warn.conflicts=FALSE)

@@

latex(format(c("Median Index"=med, "Lower Index"=lower, "Upper Index"=upper, "$\\Delta$ Gini"=dgini),digits=ndig),file="",title=title,table.env=FALSE)
}

<<polindex20032010, results='asis'>>=
polTable(bd.2010.ind,bd.2003.ind)
@
